Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-21 Manuscript/manuscript.tex

>>>>

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/density_profile_K-Na_counterions_compar_pure-ECC-POPS.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged POPS bilayers using ECC-lipids and ECC-ions.  }
\todo{Joe: this figure requires updating and polishing, but serves the purpose of “showing the data”.}
\end{figure}
